{\small
\begin{itemize}

\item[]
\begin{enlace}\label{enlace0000-1} (Pág. \pageref{enlace0000a-1})
\link{http://reproducibleresearch.net/}{http://reproducibleresearch.net/}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0000-11} (Pág. \pageref{enlace0000a-11})
\link{http://www.geogebra.org/}{http://www.geogebra.org/}
\end{enlace}


\item[]
\begin{enlace}\label{enlace0000-2} (Pág. \pageref{enlace0000a-2})
\link{http://buscon.rae.es/drae}{http://buscon.rae.es/drae}
\end{enlace}



\item[]
\begin{enlace}\label{enlace0000} (Pág. \pageref{enlace0000a})
\link{http://www.anfac.com}{http://www.anfac.com}
\end{enlace}


\item[]
\begin{enlace}\label{enlace0004} (Pág. \pageref{enlace0004a})
\link{http://es.wikipedia.org/wiki/Problema\_de\_Monty\_Hall}{http://es.wikipedia.org/wiki/Problema\_de\_Monty\_Hall}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0005} (Pág. \pageref{enlace0005a})
\link{http://en.wikipedia.org/wiki/Numb3rs}{http://en.wikipedia.org/wiki/Numb3rs}
\end{enlace}


\item[]
\begin{enlace}\label{enlace0006} (Pág. \pageref{enlace0006a})
\link{http://es.wikipedia.org/wiki/Antoine_Gombaud}{http://es.wikipedia.org/wiki/Antoine\_Gombaud}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0003} (Pág. \pageref{enlace0003a})
\link{http://es.wikipedia.org/wiki/Pierre_Simon_Laplace}{http://es.wikipedia.org/wiki/Pierre\_Simon\_Laplace}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0002} (Pág. \pageref{enlace0002a})
\link{http://es.wikipedia.org/wiki/Tri\%C3\%A1ngulo\_de\_Sierpinski}{http://es.wikipedia.org/wiki/Triángulo\_de\_Sierpinski})
\end{enlace}

\item[]
\begin{enlace}\label{enlace0001} (Pág. \pageref{enlace0001a})
\link{http://es.wikipedia.org/wiki/Kolmog\%C3\%B3rov}{http://es.wikipedia.org/wiki/Kolmogórov})
\end{enlace}


\item[]
\begin{enlace}\label{enlace0007} (Pág. \pageref{enlace0007a})
\link{http://www.ted.com/talks/peter_donnelly_shows_how_stats_fool_juries.html}{\scriptsize http://www.ted.com/talks/peter\_donnelly\_shows\_how\_stats\_fool\_juries.html}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0008} (Pág. \pageref{enlace0008a}) \link{http://es.wikipedia.org/wiki/Loter\%C3\%ADa\_Primitiva\_de\_Espa\%C3\%B1a}{ http://es.wikipedia.org/wiki/Lotería\_Primitiva\_de\_España}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0009} (Pág. \pageref{enlace0009a})
\link{http://books.google.es/books?id=Tm0FAAAAQAAJ}{books.google.es/books?id=Tm0FAAAAQAAJ}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0010} (Pág. \pageref{enlace0010a})
\link{http://en.wikipedia.org/wiki/William\_Sealy\_Gosset}{http://en.wikipedia.org/wiki/William\_Sealy\_Gosset}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0011} (Pág. \pageref{enlace0011a})
\link{http://en.wikipedia.org/wiki/Beta_function}{http://en.wikipedia.org/wiki/Beta\_function}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0012} (Pág. \pageref{enlace0012a})
 \link{http://es.wikipedia.org/wiki/Funci\%C3\%B3n_gamma}{http://es.wikipedia.org/wiki/Función\_gamma}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0013} (Pág. \pageref{enlace0013a})
 \link{https://www.statstodo.com/SSizSD_Tab.php}{https://www.statstodo.com/SSizSD\_Tab.php}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0014} (Pág. \pageref{enlace0014a})
 \link{http://en.wikipedia.org/wiki/Reference_ranges_for_blood_tests}{http://en.wikipedia.org/wiki/Reference\_ranges\_for\_blood\_tests}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0015} (Pág. \pageref{enlace0015a})
 \link{http://es.wikipedia.org/wiki/Canguro_rojo}{http://es.wikipedia.org/wiki/Canguro\_rojo}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0016} (Pág. \pageref{enlace0016a})
 \link{http://es.wikipedia.org/wiki/Uria_aalge}{http://es.wikipedia.org/wiki/Uria\_aalge}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0016-2} (Pág. \pageref{enlace0016a-2})
 \link{http://www.ine.es/}{http://www.ine.es/}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0017} (Pág. \pageref{enlace0017a})
 \link{http://en.wikipedia.org/wiki/Sim\%C3\%A9on\_Denis_Poisson}{http://en.wikipedia.org/wiki/Siméon\_Denis\_Poisson}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0036} (Pág. \pageref{enlace0036a})
	{\scriptsize Para el Ejemplo \ref{cap09:ejem:CrateresLunares} (pág. \pageref{cap09:ejem:CrateresLunares}) de los cráteres lunares, los datos provienen de la página web: \link{http://www.planetary.brown.edu/html_pages/LOLAcraters.html}{http://www.planetary.brown.edu/html\_pages/LOLAcraters.html}. Ver también \cite{head2010global} y \cite{kadish2011global}.
	}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0018} (Pág. \pageref{enlace0018a})
    {\scriptsize
 \link{https://liesandstats.wordpress.com/2008/09/26/no-one-understands-error-bars/}{https://liesandstats.wordpress.com/2008/09/26/no-one-understands-error-bars/}
 }
\end{enlace}

\item[]
\begin{enlace}\label{enlace0019} (Pág. \pageref{enlace0019a})
 \link{http://en.wikipedia.org/wiki/Ronald_Fisher}{http://en.wikipedia.org/wiki/Ronald\_Fisher}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0020} (Pág. \pageref{enlace0020a})
 \link{http://es.wikipedia.org/wiki/Cyanistes_caeruleus}{http://es.wikipedia.org/wiki/Cyanistes\_caeruleus}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0021} (Pág. \pageref{enlace0021a})
 \link{http://en.wikipedia.org/wiki/Karl\_Pearson}{http://en.wikipedia.org/wiki/Karl\_Pearson}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0022} (Pág. \pageref{enlace0022a})
 \link{http://xkcd.com/552/}{http://xkcd.com/552/}\\
 \phantom{aaaaa} Versión en español en:
    \link{http://es.xkcd.com/strips/correlacion/}{http://es.xkcd.com/strips/correlacion/}.
\end{enlace}


\item[]
\begin{enlace}\label{enlace0023} (Pág. \pageref{enlace0023a})
 \link{http://en.wikipedia.org/wiki/Francis_Anscombe}{en.wikipedia.org/wiki/Francis\_Anscombe}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0024} (Pág. \pageref{enlace0024a})
 \link{http://es.wikipedia.org/wiki/Aplicaci\%C3\%B3n\_lineal}{http://es.wikipedia.org/wiki/Aplicación\_lineal}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0025} (Pág. \pageref{enlace0025a})
{\scriptsize
 \link{http://stat.ethz.ch/R-manual/R-patched/library/datasets/html/trees.html}{http://stat.ethz.ch/R-manual/R-patched/library/datasets/html/trees.html}
 }
\end{enlace}

\item[]
\begin{enlace}\label{enlace0026} (Pág. \pageref{enlace0026a})
 \link{http://www.cis.es/cis/opencms/ES/index.html}{http://www.cis.es/cis/opencms/ES/index.html}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0027} (Pág. \pageref{enlace0027a})
 \link{http://www.ayto-daganzo.org/datos-de-interes/zona-zepa.html}{http://www.ayto-daganzo.org/datos-de-interes/zona-zepa.html}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0028} (Pág. \pageref{enlace0028a})
 \link{http://es.wikipedia.org/wiki/Otis_tarda}{http://es.wikipedia.org/wiki/Otis\_tarda}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0029} (Pág. \pageref{enlace0029a})
 \link{http://www.seomonticola.org}{http://www.seomonticola.org}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0030} (Pág. \pageref{enlace0030a})
 \link{http://www.esp.org/foundations/genetics/classical/gm-65.pdf}{www.esp.org/foundations/genetics/classical/gm-65.pdf}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0031} (Pág. \pageref{enlace0031a})
 \link{http://en.wikipedia.org/wiki/Fisher's\_exact\_test}{http://en.wikipedia.org/wiki/Fisher's\_exact\_test}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0032-1} (Pág. \pageref{enlace0032a-1})
	\link{http://es.wikipedia.org/wiki/Enfermedad\_vascular\_perif\%C3\%A9rica}{http://es.wikipedia.org/wiki/Enfermedad\_vascular\_periférica}
\end{enlace}


\item[]
\begin{enlace}\label{enlace0032} (Pág. \pageref{enlace0032a})

{\scriptsize	
\link{http://ec.europa.eu/eurostat/statistics-explained/index.php/Glossary:Material\_deprivation}{http://ec.europa.eu/eurostat/statistics-explained/index.php/Glossary:Material\_deprivation}
}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0033} (Pág. \pageref{enlace0033a})
	\link{http://en.wikipedia.org/wiki/Machine\_learning}{http://en.wikipedia.org/wiki/Machine\_learning}
\end{enlace}

\item[]
\begin{enlace}\label{enlace0034} (Pág. \pageref{enlace0034a})
\link{http://www.newscientist.com/article/mg22329814.400.html}{http://www.newscientist.com/article/mg22329814.400}
\end{enlace}


\item[]
\begin{enlace}\label{enlace0035} (Pág. \pageref{enlace0035a})
	\link{https://en.wikipedia.org/wiki/Receiver\_operating\_characteristic}{https://en.wikipedia.org/wiki/Receiver\_operating\_characteristic}
\end{enlace}


\end{itemize}
}